%-------------------------
% Resume in Latex
% Author : Aras Gungore
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\ % removed some stuff here to remove empty space
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Rowan d'Auria} \\ \vspace{3pt}
    \small
    Email: \href{mailto:rowandauria1@gmail.com}{rowandauria1@gmail.com}; Phone: 07977568388; GitHub: \href{https://github.com/rowan-dauria}{https://github.com/rowan-dauria}
\end{center}



%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Data Intensive Science, MPhil, University of Cambridge (in progress)}{2025-2026}
      {}{}
      \resumeItemListStart
        \resumeItem{\textbf{Deep Learning:} Topics include model interpretability, explainability, probabilistic machine learning.}
        \resumeItem{\textbf{Advanced Statistics:} Strong emphasis on Bayesian computation and model comparison.}
        \resumeItem{\textbf{Research Project:} Self-directed project to investigate topics such as ML model interpretability, Medical Al.}
      \resumeItemListEnd
    \resumeSubheading
      {Physics, BSc, Durham University, First Class Honours}{2017-2020}
      {}{}
      \resumeItemListStart
        \resumeItem{\textbf{Laboratory Skills and Electronics (75\%):} Automated statistical analysis, including ANOVA and regression fitting to non-linear models.}
        \resumeItem{Achieved 100\% in coding workshops, including programming Monte Carlo integrators and object-oriented random walk methods.}
        \resumeItem{\textbf{Mathematical Methods in Physics (87\%):} Demonstrated a thorough understanding of mathematical concepts such as Vector Calculus and Matrix Algebra.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%----------- RESEARCH -----------

\section{Research}
  \vspace{3pt}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Featurespace Project Lead - proposal document and oral presentation}{2023}
      {}{}
      \resumeItemListStart
        \resumeItem{Developed auto-scaling cloud database to meet variable testing capacity. Created resources accessible to diverse stakeholders, from non-technical managers to specialist engineers, outlining potential migration approaches and recommending the optimal solution.}
        \resumeItem{Considered a range of factors such as encryption requirements, long-term maintenance concerns and scaling costs.}
      \resumeItemListEnd
    \resumeSubheading
      {Computing Research Project - 6,000 word research report, poster and Q\&A}{2020}
      {}{}
      \resumeItemListStart
        \resumeItem{Full-unit independent research exploring computational statistics for simulating quantum particles, titled "Simulating Probability Amplitudes of Bound Particles with MCMC Methods".}
        \resumeItem{Placed in top 5\% of my cohort.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%----------- EMPLOYMENT -----------

\section{Employment}
  \vspace{3pt}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Solutions Engineer, Lindus Health, London}{Mar. 2025-Oct. 2025}
      {}{}
      \resumeItemListStart
        \resumeItem{Developed and deployed custom tooling to automate repetitive, high-volume tasks (eg. survey creation), significantly boosting team efficiency and reducing manual configuration time.}
        \resumeItem{Engineered an automated documentation generator and integrated it with an LLM to create a central, accessible knowledge base, which was adopted by the entire deployment team to streamline onboarding.}
        \resumeItem{Achieved rapid onboarding in two weeks to actively design and configure clinical trials, demonstrating immediate technical proficiency and contributing to project execution ahead of schedule.}
      \resumeItemListEnd
    \resumeSubheading
      {Software Developer - Deployment, Featurespace, Cambridge}{Jun. 2023-Oct. 2023}
      {}{}
      \resumeItemListStart
        \resumeItem{Owned the cloud migration of testing infrastructure for highly regulated financial software. Evaluated a range of strategies for cloud deployment.}
        \resumeItem{Delivered the project with minimal oversight whilst mastering internal codebases, gaining expertise in cloud development and creating automated tests to maximise reliability.}
        \resumeItem{Provided time critical security upgrades with no notice to ensure regulatory compliance, collaborating with multiple teams to establish efficient upgrade processes and new documentation.}
      \resumeItemListEnd
    \resumeSubheading
      {Full Stack Developer, Luminance Technologies, London}{Feb. 2022-Apr. 2023}
      {}{}
      \resumeItemListStart
        \resumeItem{Led the development of an interactive data dashboard for Luminance's flagship product, implementing a configurable interface that provides a qualitative overview of the client's data. Delivered project two weeks ahead of time.}
        \resumeItem{Played a pivotal role in securing Luminance's largest ever deal by delivering a suite of new features to tight deadlines.}
        \resumeItem{Created API functionality to enable bulk user management for companies with thousands of users.}
        \resumeItem{Took ownership of the whole development lifecycle by designing and implementing automated tests.}
      \resumeItemListEnd
    \resumeSubheading
      {Technology Specialist, Luminance Technologies, London}{Jun. 2021-Feb. 2022}
      {}{}
      \resumeItemListStart
        \resumeItem{Was instrumental in securing a large client by delivering a bespoke data migration in Python. Used Pandas and supporting packages to clean a dataset containing over 100,000 data points. Produced a high quality data source that was used to pre-train Luminance's machine learning for their business case.}
        \resumeItem{Was recommended for a software development role due to exceptional performance as a Technology Specialist.}
        \resumeItem{Having taken ownership of the Python API and custom reporting functionality, continued to support members of the previous team after transitioning to a new role.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}